---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foreman

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goals of foreman are to:

  - [Unpack](#unpacking) a package's functions to interrogate [relationships](#relationships) of the functions within it.
  - [Isolate](#subset) function scripts within a package (including the documentation for local paths)
  - [Consolidate](#consolidation) a subset of self contained functions in a file(s) to allow for focused learning on a specific package functionality.

> Given these goals it is important to state that this package is not meant to replace any parent package.

The package supports both [local packages](#local-packages) and [compiled](#compiled-library) libraries.

## Installation

``` r
remotes::install_github("foreman")
```

## Local Packages

This example will use a local fork of `purrr`.

```{r example,message=FALSE,warning=FALSE}
library(foreman)
library(ggraph)
library(igraph)
```

### Unpacking

Unpack a pacakge into a list

```{r}
x <- unpack(path = '../forks/purrr/R', warn = FALSE)
```

Click the triangle to view the contents found in `arrays.R`

```{r,results='asis'}
details::details(lapply(x$arrays.R,get_text),summary = 'arrays.R')
```

### Relationships

```{r}
x_rel <- relationship(x)
```

Relationships contained in `arrays.R`

```{r}
x_rel$arrays.R
```

Functions that `compose` calls

```{r}
relationship(x,parent = 'compose')
```

Functions who call `flatten`

```{r}
relationship(x,child = 'flatten')
```

### Convert relationships to a data.frame

```{r}
x_rel_df <- as.data.frame(x_rel)
```

Click the triangle to view the data.frame

```{r,results='asis'}
details::details(x_rel_df,summary = 'Relatives')
```

### Plotting the relationships

```{r}

graph <- igraph::graph_from_data_frame(x_rel_df,directed = TRUE)

```
 
```{r}
igraph::V(graph)$parents <- names(igraph::V(graph))
```

```{r,fig.dim=c(7,7)}
ggraph(graph) +
  geom_edge_link(
    aes(colour = file),
    arrow = grid::arrow(length = unit(0.05, "inches"))) +
  geom_node_text(aes(label = parents),size = 3) +
  labs(title = 'purrr function map', colour = 'Exported') + 
  ggplot2::theme(legend.position   = 'bottom')

```


### Subset

Subsetting Package Functions

```{r}
sub_x <- subset(x,'compose')
```

Click the triangle to view the contents found in the subset containing `compose` and the functions the it calls.


```{r,results='asis'}
details::details(lapply(sub_x,get_text),summary = 'Package subset')
```

### Consolidation

Consolidating Subsetted Functions into a File

```{r}
pack_path <- repack(sub_x)
```

Click the triangle to view the contents found in the file containing the consolidated functions.

```{r,results='asis'}
details::details(file.path(pack_path,'unpacked.R'),summary = 'Consolidated Script')
```

### Compiled Library

This example will use the installed library `future`.

Using foreman with an compiled libraries is also simple

```{r}
library(future)

unpacked_future <- unpack(ns = 'future')%>%
  relationship()%>%
  as.data.frame()

```

```{r}

graph <- igraph::graph_from_data_frame(unpacked_future,directed = TRUE)
igraph::V(graph)$parents <- names(igraph::V(graph))
igraph::V(graph)$exported <- names(igraph::V(graph))%in%ls('package:future')

```

```{r,fig.dim=c(7,7)}
ggraph(graph) +
  geom_edge_link(
    arrow = grid::arrow(length = unit(0.05, "inches")),alpha = 0.05) +
  geom_node_text(aes(colour = exported,label = parents),size = 2) +
  labs(title = 'future function map', colour = 'Exported') + 
  ggplot2::theme(legend.position   = 'bottom')
```
