---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foreman

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goals of foreman are to:

  - Unpack a package's functions to interrogate relationships of the functions within it.
  - Isolate function scripts within a package (including the documentation for local paths)
  - Enable users to repack a subset of self contained functions in a package to allow for focused learning on a specific package functionality.

> This package may cause some anxiety for package maintainers. This package is not meant to replace any parent package.

## Installation

``` r
remotes::install_github("foreman")
```

## Example

The package supports both compiled libraries and local paths. This example will use a local fork of `purrr`.

```{r example,message=FALSE,warning=FALSE}
library(foreman)
library(ggraph)
library(igraph)
library(purrr)
```

### Unpacking a pacakge into a list

```{r}
x <- unpack(path = '../forks/purrr/R', warn = FALSE)
```

Click the triangle to view the contents found in `arrays.R`

```{r,results='asis'}
details::details(lapply(x$arrays.R,get_text),summary = 'arrays.R')
```

### Relationships

```{r}
x_rel <- relationship(x)
```

Relationships contained in `arrays.R`

```{r}
x_rel$arrays.R
```

Functions that `compose` calls

```{r}
relationship(x,parent = 'compose')
```

Functions who call `flatten`

```{r}
relationship(x,child = 'flatten')
```

### Convert relationships to a data.frame

```{r}
x_rel_df <- as.data.frame(x_rel)
```

Click the triangle to view the data.frame

```{r,results='asis'}
details::details(x_rel_df,summary = 'Relatives')
```

### Plotting the relationships

```{r}

graph <- igraph::graph_from_data_frame(x_rel_df,directed = TRUE)

```
 
```{r}
igraph::V(graph)$parents <- names(igraph::V(graph))
igraph::V(graph)$exported <- is_exported(igraph::V(graph)$parents,'purrr')
```

```{r,fig.dim=c(7,7)}
ggraph(graph) +
  geom_edge_link(
    aes(colour = file),
    arrow = grid::arrow(length = unit(0.05, "inches"))) +
  geom_node_text(aes(label = parents),size = 3) +
  labs(title = 'purrr function map', colour = 'Exported') + 
  ggplot2::theme(legend.position   = 'bottom')

```


### Subsetting Package Functions

```{r}
sub_x <- subset(x,'compose')
```

Click the triangle to view the contents found in the subset containing `compose` and the packages the it calls.


```{r,results='asis'}
details::details(lapply(sub_x,get_text),summary = 'Package subset')
```

### Consolidating Subsetted Functions into a File

```{r}
pack_path <- repack(sub_x)
```

Click the triangle to view the contents found in the file containing the consolidated functions.

```{r,results='asis'}
details::details(file.path(pack_path,'unpacked.R'),summary = 'Consolidated Script')
```
